### 2023-03-08 manuscript.tex
Fixing Hudgin's et al. 2020 Zenodo ref. title [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/2ba66415ee4d5e69b7890e54bec942747e76e441.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/2ba66415ee4d5e69b7890e54bec942747e76e441/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4367090381

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/077b97a7cbbaa6291b5ae7dd0da4f671c4978aee/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/077b97a7cbbaa6291b5ae7dd0da4f671c4978aee}{SORTEE-Github-Hackathon/manuscript@077b97a}
on March 8, 2023.

>>>>

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/2ba66415ee4d5e69b7890e54bec942747e76e441/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/2ba66415ee4d5e69b7890e54bec942747e76e441}{SORTEE-Github-Hackathon/manuscript@2ba6641}
on March 8, 2023.
